---
title: "Filtering SNPs"
author: "Yuan Mou"
format: html
editor: visual
---

# Set-up

```{r Clean global environment}
remove(list = ls())
```

```{r Load packages}
library(data.table)
library(tidyverse)
```

```{r source credentials file}
# source("../credentials.r")
```

# Pre-processing of BED files of predicted genes

```{r Create file paths to predicted genes by DGLinker for each list}



analysis_folder_path <- '~/Downloads/C1/dglinker'


GWAS_predicted_genes_path <- paste0(
  analysis_folder_path,
  "~/Downloads/C1/dglinker/GWAS_predicted_genes_hg19.bed"
)

DisGeNET_predicted_genes_path <- paste0(
  analysis_folder_path,
  "~/Downloads/C1/dglinker/disgenet_predicted_genes_hg19.bed"
)

Clinvar_predicted_genes_path <- paste0(
  analysis_folder_path,
  "~/Downloads/C1/dglinker/clinvar_predicted_genes_hg19.bed"
)

Union_predicted_genes_path <- paste0(
  analysis_folder_path,
  "~/Downloads/C1/dglinker/union_predicted_genes_hg19.bed"
)
```

```{r Save path names to predicted gene coordinate files into a vector}
predicted_gene_file_paths <- c(
  GWAS_predicted_genes = GWAS_predicted_genes_path,
  DisGeNET_predicted_genes = DisGeNET_predicted_genes_path,
  Clinvar_predicted_genes = Clinvar_predicted_genes_path,
  Union_predicted_genes = Union_predicted_genes_path
)
```

```{r Read in predicted gene files}


# 加载必要的包
library(dplyr)
library(readr)

# 定义包含文件路径的向量或列表
predicted_gene_file_paths <- c("~/Downloads/C1/dglinker/GWAS_predicted_genes_hg19.bed", "~/Downloads/C1/dglinker/disgenet_predicted_genes_hg19.bed", "~/Downloads/C1/dglinker/clinvar_predicted_genes_hg19.bed" , "~/Downloads/C1/dglinker/union_predicted_genes_hg19.bed")

# 使用 read.table() 函数读取预测基因文件为数据框
GWAS_predicted_genes <- read.table("~/Downloads/C1/dglinker/GWAS_predicted_genes_hg19.bed")
DisGeNET_predicted_genes <- read.table("~/Downloads/C1/dglinker/disgenet_predicted_genes_hg19.bed")
Clinvar_predicted_genes <- read.table("~/Downloads/C1/dglinker/clinvar_predicted_genes_hg19.bed")
Union_predicted_genes <- read.table("~/Downloads/C1/dglinker/union_predicted_genes_hg19.bed")

# 检查读取的数据框
head(GWAS_predicted_genes)
head(DisGeNET_predicted_genes)
head(Clinvar_predicted_genes)
head(Union_predicted_genes)

# 修改列名
predicted_gene_files <- predicted_gene_file_paths %>% 
  map(~ read.table(.x)) %>% 
  map(
    ~ .x %>% 
      rename(
        "Chromosome" = V1,
        "Left_coordinate_hg19" = V2,
        "Right_coordinate_hg19" = V3,
        "Predicted_gene" = V4,
    
      )
  )

# Check list
predicted_gene_files %>% 
  str()

# Check result
predicted_gene_files %>% 
  map(colnames)

```

```{r Rename the columns of all the lists}
# predicted_gene_files <- predicted_gene_files %>% 
#  map(
 #   ~ .x %>% 
  #      rename(
   #       "Chromosome" = V1,
    #      "Left_coordinate_hg19" = V2,
     #     "Right_coordinate_hg19" = V3,
      #    "Predicted_gene" = V4
       #        )
    #  )

# Check result
# predicted_gene_files %>% 
#  map(colnames)
```

```{r Create function to clean chromosome column}
clean_chromosome_col <- function(df, chrom_col){
  
  # Filter out result with CHROM == "chr6_ssto_hap7"
  df <- df %>% 
    filter({{ chrom_col }} != "chr6_ssto_hap7")

  # Remove "chr" such that only chromosome number or letter is used
  df <- df %>% 
    mutate({{ chrom_col }} :=
             str_replace_all(
               string = {{ chrom_col }},
               pattern = "chr", # Replace chr with empty space
               replacement = ""
               )
           )
  
  # Turn chromosome column into a factor
  df <- df %>% 
    mutate({{ chrom_col }} :=
             factor({{ chrom_col }},
                    levels = c(
                      "1", "2", "3", "4", "5", "6", "7", "8", "9", "10", 
                      "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", 
                      "21", "22", "X", "Y"
                      )
                    )
           )
  
  # Return df with newly formatted chromosome column
  return(df)
}
```

```{r Format chromosome column in every predicted gene bed file}
predicted_gene_files <- predicted_gene_files %>% 
  map(clean_chromosome_col,
      Chromosome)

predicted_gene_files %>% 
  map(~ .x %>% 
        select(Chromosome) %>% 
        arrange(Chromosome) %>% 
        unique(.)
      )
```

```{r Filter out chromosome equal to X or Y}
predicted_gene_files <- predicted_gene_files %>% 
  map(filter,
      Chromosome != "X" & Chromosome != "Y")

# Check X and Y chromosome genes have been filtered out
predicted_gene_files %>% 
  map(count,
      Chromosome)
```

**Note:** The predicted alzheimer's disease-linked genes in the DGLinker results file, and the predicted genes listed in the bed files with their hg19 human reference genome coordinates, do not match. Therefore, we want to remove any excess genes that appear in the bed files that do not appear in the DGLinker results file so that we only have the coordinate information about the predicted alzheimer's disease-linked genes.

```{r Read in predicted genes from each gene list definition}


# 加载必要的包
library(dplyr)
library(readr)

# 定义文件路径
 predicted_genes_file_path <- "~/Downloads/C1/dglinker/Predicted_genes_summary_raw.csv"

# 读取 CSV 文件
predicted_alzheimer_genes <- read_csv(predicted_genes_file_path)

# 检查数据维度
predicted_alzheimer_genes %>% 
  dim()

# 查看数据的前几行
predicted_alzheimer_genes %>% 
  head()



```

```{r Create list of predicted alzheimer genes with NAs removed}
# For each column, remove NA's and save in list format
predicted_alzheimer_gene_list <- predicted_alzheimer_genes %>% 
  map(~ na.omit(.x))


# 加载必要的包
library(dplyr)
library(purrr)

# 假设 predicted_alzheimer_genes 是之前读取的数据框

# For each column, remove NA's and save in list format
predicted_alzheimer_gene_list <- predicted_alzheimer_genes %>% 
  map(~ na.omit(.x))

# 创建与列数量相匹配的名称列表
gene_list_names <- c(
  "GWAS",
  "DisGeNET",
  "Clinvar",
  "Union"
)

# 校验名称数量是否与列表中的列数量相匹配
if (length(gene_list_names) == ncol(predicted_alzheimer_genes)) {
  names(predicted_alzheimer_gene_list) <- gene_list_names
} else {
  print("Number of names doesn't match number of columns")
}

# 检查列表
predicted_alzheimer_gene_list %>% 
  str()





```

```{r Remove predicted genes from bed files that are not in DGLinker results}
# Filter genes in each bed file to ones appearing in predicted genes by DGLinker
predicted_gene_files <- predicted_gene_files %>% 
  map2(predicted_alzheimer_gene_list,
       ~ .x %>% 
        filter(Predicted_gene %in% .y))

# Check N genes for each list
predicted_gene_files %>% 
  map(nrow)
```

```{r Save all of the individual tibbles to the global environment}


for (i in seq_along(predicted_gene_files)) {
  assign(gene_list_names[i], predicted_gene_files[[i]], envir = .GlobalEnv)
}

```

# Find common predicted genes

We also want to perform a GWAS validation of the genes that have been predicted to be associated with alzheimer in every list. Therefore, we need to make a df containing the genes that were predicted to be associated with alzheimer in every list.

```{r Create df with genes predicted to be linked to alzheimer in every list}


# Find the intersection of the four gene lists
common_predicted_genes <- Reduce(intersect, predicted_gene_files) %>% 
  as_tibble()


# Check
common_predicted_genes %>% 
  dim()

common_predicted_genes %>% 
  head()
```

# BED files: Remove genes with duplicate start/end transcripts

```{r Create function to find genes with duplicate start/end transcripts}


find_duplicated_coords <- function(df){
  duplicated_coords_summary <- df %>% 
    rename(
      "Chromosome" = V1,
      "Left_coordinate_hg19" = V2,
      "Right_coordinate_hg19" = V3,
      "Predicted_gene" = V4
    ) %>% 
    group_by(Chromosome, Left_coordinate_hg19, Right_coordinate_hg19) %>% 
    mutate(duplicate = n() > 1) %>% 
    ungroup() %>% 
    filter(duplicate == TRUE) %>% 
    arrange(desc(Left_coordinate_hg19))
  
  return(duplicated_coords_summary)
}


```

```{r Create not in function}
'%not_in%' <- Negate('%in%')
```

## GWAS BED file

```{r Find predicted genes with duplicated coordinates in GWAS list}


find_duplicated_coords(
  df = GWAS_predicted_genes
)


```

```{r Remove duplicated predicted genes in GWAS list}


# 创建要删除的重复基因列表
duplicate_GWAS_pred_genes <- c(
 
)

# 使用正确的列名进行重命名
colnames(GWAS_predicted_genes) <- c(
  "Chromosome",
  "Left_coordinate_hg19",
  "Right_coordinate_hg19",
  "Predicted_gene"
)

# 在 GWAS 预测基因列表中过滤掉重复的基因
GWAS_predicted_genes <- GWAS_predicted_genes %>% 
  filter(!(Predicted_gene %in% duplicate_GWAS_pred_genes))

# 检查是否成功删除重复基因
duplicate_GWAS_pred_genes %in% GWAS_predicted_genes$Predicted_gene


```

## DisGeNET BED file

```{r Find predicted genes with duplicated coordinates in DisGeNET list}
find_duplicated_coords(
  df = DisGeNET_predicted_genes
)
```

```{r Remove duplicated predicted genes in DisGeNET list}
# Create vector of duplicated genes
duplicate_DisGeNET_pred_genes <- c(
  "NME1",
  "NME2",
  "IGF2",
  "INS"
)

# 使用正确的列名进行重命名
colnames(DisGeNET_predicted_genes) <- c(
  "Chromosome",
  "Left_coordinate_hg19",
  "Right_coordinate_hg19",
  "Predicted_gene"
)



DisGeNET_predicted_genes <- DisGeNET_predicted_genes %>% 
   filter(!(Predicted_gene %in% duplicate_DisGeNET_pred_genes))

# Check
duplicate_DisGeNET_pred_genes %in% DisGeNET_predicted_genes$Predicted_gene
```

## Clinvar BED file

```{r Find predicted genes with duplicated coordinates in Clinvar list}
find_duplicated_coords(
  df = Clinvar_predicted_genes
)
```

```{r Remove duplicated predicted genes in Clinvar list}
# Create vector of duplicated genes
duplicate_Clinvar_pred_genes <- c(
  "IGF2",
  "INS"
)

# 使用正确的列名进行重命名
colnames(Clinvar_predicted_genes) <- c(
  "Chromosome",
  "Left_coordinate_hg19",
  "Right_coordinate_hg19",
  "Predicted_gene"
)

Clinvar_predicted_genes <- Clinvar_predicted_genes %>% 
  filter(Predicted_gene %not_in% duplicate_Clinvar_pred_genes)

# Check
duplicate_Clinvar_pred_genes %in% Clinvar_predicted_genes$Predicted_gene
```

## Union BED file

```{r Find predicted genes with duplicated coordinates in Union list}
find_duplicated_coords(
  df = Union_predicted_genes
)
```

```{r Remove duplicated predicted genes in Union list}
# Create vector of duplicated genes
duplicate_Union_pred_genes <- c(
  
)

# 使用正确的列名进行重命名
colnames(Union_predicted_genes) <- c(
  "Chromosome",
  "Left_coordinate_hg19",
  "Right_coordinate_hg19",
  "Predicted_gene"
)

Union_predicted_genes <- Union_predicted_genes %>% 
  filter(Predicted_gene %not_in% duplicate_Union_pred_genes)

# Check
duplicate_Union_pred_genes %in% Union_predicted_genes$Predicted_gene
```

```{r Read in the known genes that were submitted to DGLinker for each list}
training_genes <- read_csv("~/Downloads/C1/dglinker/predicted-Alzherimer-genes.csv")


training_genes <- training_genes %>% 
  map(~ na.omit(.x))

# Rename list headers
training_gene_list_names <- c(
  "GWAS_training_genes",
  "DisGeNET_training_genes",
  "Clinvar_training_genes",
  "Union_training_genes"
)

names(training_genes) <- training_gene_list_names

training_genes %>% 
  str()
```

```{r Check whether predicted genes are in the training genes for each list}
GWAS_predicted_genes$Predicted_gene %in% training_genes$GWAS_training_genes %>% 
  summary()

DisGeNET_predicted_genes$Predicted_gene %in% training_genes$DisGeNET_training_genes %>% 
  summary()

Clinvar_predicted_genes$Predicted_gene %in% training_genes$Clinvar_training_genes %>% 
  summary()

Union_predicted_genes$Predicted_gene %in% training_genes$Union_training_genes %>% 
  summary()
```

## Common predicted genes BED file

*Note:* All genes in common predicted genes are unique. No duplicates to be removed.

```{r Find genes with duplicated coordinates in common predicted genes}

common_predicted_genes <- common_predicted_genes
  col_names = TRUE  

  
duplicated_coords_summary <- common_predicted_genes %>% 
  group_by(Chromosome, Left_coordinate_hg19, Right_coordinate_hg19) %>% 
  mutate(duplicate = n() > 1) %>% 
  ungroup() %>% 
  filter(duplicate == TRUE) %>% 
  arrange(desc(Left_coordinate_hg19))



# Check genes in common predicted genes are unique
length(unique(common_predicted_genes$Predicted_gene)) == length(common_predicted_genes$Predicted_gene)

```

# Pre-processing alzheimer GWAS summary data

```{r Read GWAS summary statistics data}
# CORE PGC dataset
GWAS_summary_statistics <- read_csv("~/Downloads/C1/gwas validation/Data Sheet 2.csv")
 

# Check
GWAS_summary_statistics %>% 
  dim()

GWAS_summary_statistics %>% 
  head()
```

```{r Check how many unique SNPs are in the GWAS summary statistics}
# Find unique SNPs in GWAS summary stats and get SNP count
unique_snps_count <- unique(GWAS_summary_statistics$ID) %>% 
  length()

# Check whether unique SNP count is equal to the no. of rows in original file
unique_snps_count
unique_snps_count == nrow(GWAS_summary_statistics) # TRUE
```

```{r Check NA's in GWAS summary stats}
# Check overall missignness
sum(is.na(GWAS_summary_statistics))

# Check no. of missing values in POS column
sum(is.na(GWAS_summary_statistics$POS))

# Inspect row with missig POS value
GWAS_summary_statistics %>% 
  filter(is.na(POS))

# Remove row with all NA values
GWAS_summary_statistics <- GWAS_summary_statistics %>% 
  filter(!is.na(POS))

# Check
GWAS_summary_statistics %>% 
  dim()
```

```{r Check distribution of chromosome in GWAS summary stats}
# Turn off scientific notation for plot
options(scipen = 999)



GWAS_summary_statistics %>% 
  count(chr) %>% 
  na.omit() %>% 
  ggplot(aes(x = chr, y = n)) +
  geom_bar(stat = "identity",
           fill = "#EFC10B",
           colour = "Black") +
  labs(title = "No. of SNPs at each chromosome in GWAS summary statistics") +
  theme_minimal() +
  scale_x_discrete() +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))


```

```{r Create copy of alzheimer GWAS summary stats for each chromosome}
# Create vector of chromosome numbers to use in filter
chr_numbers <- 1:22

# Create list of df's for SNPs from each chromosome
GWAS_summary_statistics_list <- chr_numbers %>% 
  map( ~ GWAS_summary_statistics %>% 
         filter(chr == .x))

# Check dimensions match graph above
GWAS_summary_statistics_list %>% 
  map(dim)
```

```{r Name each df in the GWAS summary statistics list}
# Create vector of names
df_names <- paste0("GWAS_summary_stats_chr", 1:22)

# Rename df's in the list and add ID column
for (i in seq_along(GWAS_summary_statistics_list)) {
  df <- GWAS_summary_statistics_list[[i]]
  df <- df %>%
    mutate(ID = ID)
  GWAS_summary_statistics_list[[i]] <- df
}


# Rename df's in the list
names(GWAS_summary_statistics_list) <- df_names

# Check
GWAS_summary_statistics_list %>% 
  names()



```

```{r Save individual tibbles to global environment}
list2env(GWAS_summary_statistics_list, .GlobalEnv)
```

# Create intersection files for SNP2GENE

```{r Create function to filter SNPs mapping to predicted genes}

filter_SNPs <- function(chromosome, left_coordinate, right_coordinate){
 
SNP_filter_list <- NULL
 
   
  if(chromosome == "chr1"){ # If predicted gene is located on the first chromosome
    SNP_filter_list <- GWAS_summary_stats_chr1 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr1
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  
  } else if(chromosome == "chr2"){
    SNP_filter_list <- GWAS_summary_stats_chr2 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr2
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
     
    
  } else if(chromosome == "chr3"){
    SNP_filter_list <- GWAS_summary_stats_chr3 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr3
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
       ) 
    
  } else if(chromosome == "chr4"){
    SNP_filter_list <- GWAS_summary_stats_chr4 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr4
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr5"){
    SNP_filter_list <- GWAS_summary_stats_chr5 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr5
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr6"){
    SNP_filter_list <- GWAS_summary_stats_chr6 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr6
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr7"){
    SNP_filter_list <- GWAS_summary_stats_chr7 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr7
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr8"){
    SNP_filter_list <- GWAS_summary_stats_chr8 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr8
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr9"){
    SNP_filter_list <- GWAS_summary_stats_chr9 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr9
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr10"){
    SNP_filter_list <- GWAS_summary_stats_chr10 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr10
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr11"){
    SNP_filter_list <- GWAS_summary_stats_chr11 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr11
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr12"){
    SNP_filter_list <- GWAS_summary_stats_chr12 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr12
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr13"){
    SNP_filter_list <- GWAS_summary_stats_chr13 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr13
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr14"){
    SNP_filter_list <- GWAS_summary_stats_chr14 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr14
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr15"){
    SNP_filter_list <- GWAS_summary_stats_chr15 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr15
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr16"){
    SNP_filter_list <- GWAS_summary_stats_chr16 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr16
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr17"){
    SNP_filter_list <- GWAS_summary_stats_chr17 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr17
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr18"){
    SNP_filter_list <- GWAS_summary_stats_chr18 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr18
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr19"){
    SNP_filter_list <- GWAS_summary_stats_chr19 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr19
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr20"){
    SNP_filter_list <- GWAS_summary_stats_chr20 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr20
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr21"){
    SNP_filter_list <- GWAS_summary_stats_chr21 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr21
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
    
  } else if(chromosome == "chr22"){
    SNP_filter_list <- GWAS_summary_stats_chr22 %>% 
      filter( # Filter SNPs within start/end transcript of predicted gene on chr22
      dplyr::between(
        POS, 
        left = left_coordinate,
        right = right_coordinate
        )
      )
  }
  
  
  # Add ID column to the filtered SNP data
  # if (!is.null(SNP_filter_list)) {
  #   SNP_filter_list <- SNP_filter_list %>% mutate(ID = GWAS_summary_statistics$ID)
#   }


  # Return list of df's with filtered SNPs
  return(SNP_filter_list)
}


```

```{r Perform intersection for GWAS predicted genes}

# Create list of input for filter_SNPs function
GWAS_input_list <- list(
  chromosome = GWAS_predicted_genes$Chromosome,
  left_coordinate = GWAS_predicted_genes$Left_coordinate_hg19,
  right_coordinate = GWAS_predicted_genes$Right_coordinate_hg19
)

# Perform intersection
GWAS_list_SNPs <- GWAS_input_list %>% 
  pmap(filter_SNPs) %>% 
  rbindlist(use.names = TRUE) %>% 
  distinct(ID, .keep_all = TRUE)

  
# Check new SNPs df
dim(GWAS_list_SNPs) 

head(GWAS_list_SNPs)

```

```{r Perform intersection for DisGeNET predicted genes}
# Create list of input for filter_SNPs function
DisGeNET_input_list <- list(
  chromosome = DisGeNET_predicted_genes$Chromosome, 
  left_coordinate = DisGeNET_predicted_genes$Left_coordinate_hg19,
  right_coordinate = DisGeNET_predicted_genes$Right_coordinate_hg19
)

# Perform intersection
DisGeNET_list_SNPs <- DisGeNET_input_list %>% 
  pmap(filter_SNPs) %>% 
  rbindlist(use.names = TRUE) %>%   # Bind df's by matching column names
  distinct(ID, .keep_all = TRUE)    # Get all distinct SNPs and keep all other columns

# Check new SNPs df
dim(DisGeNET_list_SNPs)
head(DisGeNET_list_SNPs)

```

```{r Perform intersection for Clinvar predicted genes}
# Create list of input for filter_SNPs function
Clinvar_input_list <- list(
  chromosome = Clinvar_predicted_genes$Chromosome,
  left_coordinate = Clinvar_predicted_genes$Left_coordinate_hg19,
  right_coordinate = Clinvar_predicted_genes$Right_coordinate_hg19
)

# Perform intersection
Clinvar_list_SNPs <- Clinvar_input_list %>% 
  pmap(filter_SNPs) %>% 
  rbindlist(use.names = TRUE) %>%  # Bind df's by matching column names
  distinct(ID, .keep_all = TRUE) # Get all distinct SNPs and keep all other columns


# Check new SNPs df
 dim(Clinvar_list_SNPs) 
 
 head(Clinvar_list_SNPs)



```

```{r Perform intersection for Union predicted genes}
# Create list of input for filter_SNPs function
Union_input_list <- list(
  chromosome = Union_predicted_genes$Chromosome,
  left_coordinate = Union_predicted_genes$Left_coordinate_hg19,
  right_coordinate = Union_predicted_genes$Right_coordinate_hg19
)

# Perform intersection
Union_list_SNPs <- Union_input_list %>% 
  pmap(filter_SNPs) %>% 
  rbindlist(use.names = TRUE)%>%   # Bind df's by matching column names
   distinct(ID, .keep_all = TRUE) # Get all distinct SNPs and keep all other columns

# Check new SNPs df

  dim(Union_list_SNPs ) 


  head(Union_list_SNPs )
```

```{r Perform intersection for common predicted genes across lists}
# Create list of input for filter_SNPs function
common_predicted_gene_input_list <- list(
  chromosome = common_predicted_genes$Chromosome,
  left_coordinate = common_predicted_genes$Left_coordinate_hg19,
  right_coordinate = common_predicted_genes$Right_coordinate_hg19
)

# Perform intersection
common_predicted_gene_SNPs <- common_predicted_gene_input_list %>% 
  pmap(filter_SNPs) %>% 
  rbindlist(use.names = TRUE)%>%   # Bind df's by matching column names
  distinct(ID, .keep_all = TRUE) # Get all distinct SNPs and keep all other columns

# Check new SNPs df

  dim(common_predicted_gene_SNPs) 

  head(common_predicted_gene_SNPs)

  
```

## Save Intersection files

```{r Save GWAS intersection file}
library(readr)
write_csv(
  GWAS_list_SNPs,
  file = "~/Downloads/C1/dglinker/Filtered_GWAS_SNPs:GWAS_SNPs.csv"
)


```

```{r Save DisGeNET intersection file}
library(readr)
write_csv(
  DisGeNET_list_SNPs,
  file = "~/Downloads/C1/dglinker/Filtered_GWAS_SNPs:DisGeNET_SNPs.csv"
)

```

```{r Save Clinvar intersection file}
library(readr)
write_csv(
  Clinvar_list_SNPs,
  file = "~/Downloads/C1/dglinker/Filtered_GWAS_SNPs:Clinvar_SNPs.csv"
)
```

```{r Save Union intersection file}
library(readr)
write_csv(
  Union_list_SNPs,
  file = "~/Downloads/C1/dglinker/Filtered_GWAS_SNPs:Union_SNPs.csv"
)
```

```{r Save common predicted genes intersection file}
write_csv(
  common_predicted_gene_SNPs,
  file = paste0(
    analysis_folder_path,
    "Filtered_GWAS_SNPs/Common_predicted_gene_SNPs.csv"
  )
)
```
