---
title: "Figures"
author: "Yuan Mou"
format: html
editor: visual
---

# Set-up

```{r Clean global environment}
remove(list=ls())
```

```{r Install ggVennDiagram package}
#ggVennDiagram - making venn diagrams in R
# devtools::install_github("gaospecial/ggVennDiagram")

# sf - To support the venn diagram plotting
#install.packages("sf")
```

```{r Load Packages}
library(ggVennDiagram)
library(sf)
library(tidyverse)
```

```{r Source credentials file}
# source("../credentials.r")
```

# Create input Alzheimer venn diagram

## Pre-processing

```{r Create paths to files specifying the input genes to DGLinker for each list}

analysis_folder_path <- '/Downloads/C1/Venn'


GWAS_input_genes_path <- paste0(
  analysis_folder_path, 
  "~/Downloads/C1/Venn /GWAS_DGLinker_input_genes.csv "
  )

DisGeNET_input_genes_path <- paste0(
  analysis_folder_path,
  "~/Downloads/C1/Venn /DisGeNET_DGLinker_input_genes.csv "
)

Clinvar_input_genes_path <- paste0(
  analysis_folder_path,
  "~/Downloads/C1/Venn /Clinvar_DGLinker_input_genes.csv "
)

Union_input_genes_path <- paste0(
  analysis_folder_path,
  " ~/Downloads/C1/Venn /Union_DGLinker_input_genes.csv"
)
```

```{r Create named vector with file path to input DGLinker genes}
input_DGLinker_gene_paths <- c(
  GWAS = GWAS_input_genes_path,
  DisGeNET = DisGeNET_input_genes_path,
  Clinvar = Clinvar_input_genes_path,
  Union = Union_input_genes_path
)
```

```{r Read in DGLinker input genes}

# 加载必要的包
library(dplyr)
library(readr)

# 定义包含文件路径的向量或列表
 input_DGLinker_gene_paths <- c("~/Downloads/C1/Venn /GWAS_DGLinker_input_genes.csv", "~/Downloads/C1/Venn /DisGeNET_DGLinker_input_genes.csv", "~/Downloads/C1/Venn /Clinvar_DGLinker_input_genes.csv" , "~/Downloads/C1/Venn /Union_DGLinker_input_genes.csv")


# 使用map读取文件
DGLinker_input_genes<-map(input_DGLinker_gene_paths, read.csv)


# Check
DGLinker_input_genes %>% 
  map(head)


```

```{r Put one gene per cell}
DGLinker_input_genes <- DGLinker_input_genes %>% 
  map(~ .x %>% 
        separate_rows(DGLinker_input_genes,
                      sep = ", ")
      )

# Check
DGLinker_input_genes %>% 
  map(head)
```

```{r Covert the dataframes into vectors}
DGLinker_input_genes <- DGLinker_input_genes %>% 
  map(~ .x %>% 
        pull(DGLinker_input_genes))

# Check
DGLinker_input_genes %>% 
  map(head)
```

```{r Count no. of input genes per list}
DGLinker_input_genes %>% 
  map(length)
```

## Venn diagram plot

```{r Create venn diagram for input schizophrenia genes}

# Rename list headers
gene_list_names <- c(
  "GWAS",
  "DisGeNET",
  "Clinvar",
  "Union"
)

names(DGLinker_input_genes) <- gene_list_names

input_gene_venn <- Venn(DGLinker_input_genes[-4])
d <- process_data(input_gene_venn)

d2 <- process_data(input_gene_venn)
d2@region <- st_polygonize(d@setEdge)

# Create vector with colours for lists in plot
colours <- c(
  GWAS = 'blue', 
  DisGeNET = 'red',
  Clinvar = 'green',
  Union = 'orange'
)

# Create venn diagram
ggplot() +
  geom_sf(aes(fill = name), data = venn_region(d2)) +
  geom_sf(aes(color = name), data = venn_setedge(d)) +
  geom_sf_text(aes(label = name), size = 3.2, data = venn_setlabel(d)) +
  geom_sf_text(aes(label = count), data = venn_region(d)) +
  scale_color_manual(values = alpha(colours[-4], .2)) +
  scale_fill_manual(values = alpha(colours[-4], .2)) +
  theme_void() +
  theme(legend.title = element_blank(),
        legend.position="top",
        legend.justification = "center")
```

```{r}
genes <- unique(c(DGLinker_input_genes$GWAS, DGLinker_input_genes$DisGeNET, DGLinker_input_genes$Clinvar,DGLinker_input_genes$Union))


dta <- data.frame(genes)
dta$label1 <- 0
dta$label2 <- 0
dta$label3 <- 0
dta$label4 <- 0
for (i in 1:nrow(dta)){
  dta[i,]$label1 <- dta[i,]$genes %in% DGLinker_input_genes$GWAS
  dta[i,]$label2 <- dta[i,]$genes %in% DGLinker_input_genes$DisGeNET
  dta[i,]$label3 <- dta[i,]$genes %in% DGLinker_input_genes$Clinvar
  dta[i,]$label4 <- dta[i,]$genes %in% DGLinker_input_genes$Union
}

oneplus2 <- dta %>% 
  filter(label1 == 1 & label2 == 1) %>% 
  select(genes)
oneplus3 <- dta %>% 
  filter(label1 == 1 & label3 == 1) %>% 
  select(genes)
twoplus3 <- dta %>% 
  filter(label2 == 1 & label3 == 1) %>% 
  select(genes)

all <- dta %>% 
  filter(label1 == 1 & label1 == 1 & label3 == 1) %>% 
  select(genes)

max_length <- max(length(oneplus2$genes), length(oneplus3$genes), length(twoplus3$genes), length(all$genes))
GWAS_DisGeNet <- c(oneplus2$genes, rep(NA, max_length - length(oneplus2$genes)))
GWAS_Clinvar <- c(oneplus3$genes, rep(NA, max_length - length(oneplus3$genes)))
Clinvar_DisGeNet <- c(twoplus3$genes, rep(NA, max_length - length(twoplus3$genes)))
all_have <- c(all$genes, rep(NA, max_length - length(all$genes)))

dta.out <- data.frame(GWAS_DisGeNet, GWAS_Clinvar, Clinvar_DisGeNet, all_have)
write.csv(dta.out, "~/Downloads/C1/Venn /first-venn-genes.csv ")
```

## Predicted Alzheimer genes diagram

```{r Read in predicted genes from each gene list definition}


 predicted_Alzheimer_genes <- read_csv("~/Downloads/C1/Venn /predicted-Alzherimer-genes.csv")
 paste0(
     analysis_folder_path,
     "~/Downloads/C1/Venn /predicted-Alzherimer-genes.csv"
   )
 

file_path <- "~/Downloads/C1/Venn /predicted-Alzherimer-genes.csv"

# 读取CSV文件数据
data <- read.csv(file_path)


# 查看数据的前几行
head(data)


# Check

# 查看数据框的维度
predicted_Alzheimer_genes %>% 
  dim()

# 查看数据框的前几行数据
predicted_Alzheimer_genes %>% 
  head()

# 使用逗号作为分隔符，将GWAS列的多个值拆分为多行
predicted_Alzheimer_genes <- predicted_Alzheimer_genes %>% 
  separate_rows(GWAS, sep = ",")

# 使用连字符作为分隔符，将GWAS列的多个值拆分为多行
predicted_Alzheimer_genes <- predicted_Alzheimer_genes %>% 
  separate_rows(GWAS, sep = "-")


```

```{r Create list of predicted Alzheimer genes with NAs removed}
# For each column, remove NA's and save in list format


predicted_Alzheimer_gene_list <- predicted_Alzheimer_genes %>% 
  map(~ na.omit(.x))




# Rename list headers
gene_list_names <- c(
  "GWAS",
  "DisGeNET",
  "Clinvar",
  "Union"
)

names(predicted_Alzheimer_gene_list) <- gene_list_names

# Check list
predicted_Alzheimer_gene_list %>% 
  str()
```

```{r Check that there's no missingness in the predicted gene vectors}
predicted_Alzheimer_gene_list %>% 
  map(~sum(is.na(.x)))
```

```{r Check how many genes were predicted by each definition list}
predicted_Alzheimer_gene_list %>% 
  map(length)
```

```{r}
genes <- unique(c(predicted_Alzheimer_gene_list$predicted_Alzheimer_genes, predicted_Alzheimer_genes$GWAS, predicted_Alzheimer_genes$DisGeNET,predicted_Alzheimer_genes$Clinvar))
dta <- data.frame(genes)
dta$label1 <- 0
dta$label2 <- 0
dta$label3 <- 0
dta$label4 <- 0

for (i in 1:nrow(dta)){
  dta[i,]$label1 <- dta[i,]$genes %in% predicted_Alzheimer_genes$GWAS
  dta[i,]$label2 <- dta[i,]$genes %in% predicted_Alzheimer_genes$DisGeNET
  dta[i,]$label3 <- dta[i,]$genes %in% predicted_Alzheimer_genes$Clinvar
  dta[i,]$label4 <- dta[i,]$genes %in% predicted_Alzheimer_genes$Union
 
}

  
ab <- dta %>% 
  filter(label1 == 1 & label2 == 1) %>% 
  select(genes)

ac <- dta %>% 
  filter(label1 == 1 & label3 == 1) %>% 
  select(genes)
ad <- dta %>% 
  filter(label1 == 1 & label4 == 1) %>% 
  select(genes)
bc <- dta %>% 
  filter(label2 == 1 & label3 == 1) %>% 
  select(genes)
bd <- dta %>% 
  filter(label2 == 1 & label4 == 1) %>% 
  select(genes)
cd <- dta %>% 
  filter(label3 == 1 & label4 == 1) %>% 
  select(genes)

abc <- dta %>% 
  filter(label1 == 1 & label2 == 1 & label3 == 1) %>% 
  select(genes)

abd <- dta %>% 
  filter(label1 == 1 & label2 == 1 & label4 == 1) %>% 
  select(genes)

acd<- dta %>% 
  filter(label1 == 1 & label3 == 1 & label4 == 1) %>% 
  select(genes)


bcd <- dta %>% 
  filter(label2 == 1 & label3 == 1 & label4 == 1) %>% 
  select(genes)


abcd <- dta %>% 
  filter(label1 == 1 & label2 == 1 & label3 == 1 & label4 == 1) %>% 
  select(genes)

all <- dta %>% 
  filter(label1 == 1 & label1 == 1 & label3 == 1 & label4 == 1) %>% 
  select(genes)

max_length <- max(length(ab$genes), length(ac$genes), length(ad$genes), length(ad$genes), length(bc$genes),length(bd$genes),length(cd$genes))

ab <- c(ab$genes, rep(NA, max_length - length(ab$genes)))
ac<- c(ac$genes, rep(NA, max_length - length(ac$genes)))
ad<- c(ad$genes, rep(NA, max_length - length(ad$genes)))

bc<- c(bc$genes, rep(NA, max_length - length(bc$genes)))
bd<- c(bd$genes, rep(NA, max_length - length(bd$genes)))

cd<- c(cd$genes, rep(NA, max_length - length(cd$genes)))

abc<- c(abc$genes, rep(NA, max_length - length(abc$genes)))
abd<- c(abd$genes, rep(NA, max_length - length(abd$genes)))

acd<- c(acd$genes, rep(NA, max_length - length(acd$genes)))

all <- c(all$genes, rep(NA, max_length - length(all$genes)))



dta.out <- data.frame(ab,ac,ad,bc,bd,cd,abc,abd,acd,all)
write.csv(dta.out, "~/Downloads/C1/Venn /second-venn-genes.csv")

```

```{r Create venn diagram for predicted schizophrenia genes}
predicted_gene_venn <- Venn(predicted_Alzheimer_gene_list)
d_predicted <- process_data(predicted_gene_venn)

d2_predicted <- process_data(predicted_gene_venn)
d2_predicted@region <- st_polygonize(d_predicted@setEdge)

# Create venn diagram
ggplot() +
  geom_sf(aes(fill = name), data = venn_region(d2_predicted)) +
  geom_sf(aes(color = name), data = venn_setedge(d_predicted)) +
  geom_sf_text(aes(label = name), size = 3.2, data = venn_setlabel(d_predicted)) +
  geom_sf_text(aes(label = count), data = venn_region(d_predicted)) +
  scale_color_manual(values = alpha(colours, .2)) +
  scale_fill_manual(values = alpha(colours, .2)) +
  theme_void() +
  theme(legend.title = element_blank())
```

## Predicted and input gene overlap graph

Finally, a stacked bar graph will be created to show the overlap between the genes that were predicted after each list submission to DGLinker and the input genes in the other lists.

For each of these predictions, I need to break them down into:

-   The predicted genes that appear in the input of at least one other list
-   The predicted genes that do not appear in the input of at least one other list

```{r Check how many of the GWAS gene predictions were present in each input list}
GWAS_in_DisGeNET <- predicted_Alzheimer_gene_list$GWAS %in% DGLinker_input_genes$DisGeNET
GWAS_in_Clinvar <- predicted_Alzheimer_gene_list$GWAS %in% DGLinker_input_genes$Clinvar
GWAS_in_Union <- predicted_Alzheimer_gene_list$GWAS %in% DGLinker_input_genes$Union

# Check summaries
GWAS_in_DisGeNET %>% 
  summary()

GWAS_in_Clinvar %>% 
  summary()

GWAS_in_Union %>% 
  summary()
```

```{r Check total of GWAS predicted genes in all other input lists}
# Collapse the boolean vectors into one, same length vector where if any are TRUE, then TRUE, else FALSE
GWAS_pred_input_overlap <- Reduce(
  "|", 
  list(
    GWAS_in_DisGeNET,
    GWAS_in_Clinvar,
    GWAS_in_Union
    )
  ) %>% 
  summary()

# Check
GWAS_pred_input_overlap
```

```{r Check how many of the DisGeNET gene predictions were present in each input list}
DisGeNET_in_GWAS <- predicted_Alzheimer_gene_list$DisGeNET %in% DGLinker_input_genes$GWAS
DisGeNET_in_Clinvar <- predicted_Alzheimer_gene_list$DisGeNET %in% DGLinker_input_genes$Clinvar
DisGeNET_in_Union <- predicted_Alzheimer_gene_list$DisGeNET %in% DGLinker_input_genes$Union

# Check summaries
DisGeNET_in_GWAS %>% 
  summary()

DisGeNET_in_Clinvar %>% 
  summary()

DisGeNET_in_Union %>% 
  summary()
```

```{r Check total of DisGeNET predicted genes in all other input lists}
# Collapse the boolean vectors into one, same length vector where if any are TRUE, then TRUE, else FALSE
DisGeNET_pred_input_overlap <- Reduce(
  "|", 
  list(
    DisGeNET_in_GWAS,
    DisGeNET_in_Clinvar,
    DisGeNET_in_Union
    )
  ) %>% 
  summary()

# Check
DisGeNET_pred_input_overlap
```

```{r Check how many of the Clinvar gene predictions were present in each input list}
Clinvar_in_GWAS <- predicted_Alzheimer_gene_list$Clinvar %in% DGLinker_input_genes$GWAS
Clinvar_in_DisGeNET <- predicted_Alzheimer_gene_list$Clinvar %in% DGLinker_input_genes$DisGeNET
Clinvar_in_Union <- predicted_Alzheimer_gene_list$Clinvar %in% DGLinker_input_genes$Union

# Check summaries
Clinvar_in_GWAS %>% 
  summary()

Clinvar_in_DisGeNET %>% 
  summary()

Clinvar_in_Union %>% 
  summary()
```

```{r Check total of Clinvar predicted genes in other input lists}
# Collapse the boolean vectors into one, same length vector where if any are TRUE, then TRUE, else FALSE
Clinvar_pred_input_overlap <- Reduce(
  "|", 
  list(
    Clinvar_in_GWAS,
    Clinvar_in_DisGeNET,
    Clinvar_in_Union
    )
  ) %>% 
  summary()

# Check
Clinvar_pred_input_overlap
```

```{r Check how many of the Union gene predictions were present in each input list}
Union_in_GWAS <- predicted_Alzheimer_gene_list$Union %in% DGLinker_input_genes$GWAS
Union_in_DisGeNET <- predicted_Alzheimer_gene_list$Union %in% DGLinker_input_genes$DisGeNET
Union_in_Clinvar <- predicted_Alzheimer_gene_list$Union %in% DGLinker_input_genes$Clinvar

# Collapse the boolean vectors into one, same length vector where if any are TRUE, then TRUE, else FALSE
Union_pred_input_overlap <- Reduce(
  "|", 
  list(
    Union_in_GWAS,
    Union_in_DisGeNET,
    Union_in_Clinvar
    )
  ) %>% 
  summary()

# Check
Union_pred_input_overlap
```

```{r Create tibble with results}
predicted_input_gene_overlap <- tibble(
  gene_list = c(
    "GWAS",
    "DisGeNET",
    "Clinvar",
    "Union"
  ),
  non_overlapping_predictions = c(
    GWAS_pred_input_overlap[2],
    DisGeNET_pred_input_overlap[2],
    Clinvar_pred_input_overlap[2],
    Union_pred_input_overlap[2]
  ),
  overlapping_predictions = c(
    GWAS_pred_input_overlap[3],
    DisGeNET_pred_input_overlap[3],
    Clinvar_pred_input_overlap[3],
    Union_pred_input_overlap[3]
  #  0 # Union predictions overlapping with input is 0 by default
  )
)

# Check
predicted_input_gene_overlap %>% 
  head()
```

```{r Reshape the predicted and input df to long format}
predicted_input_gene_overlap <- predicted_input_gene_overlap %>% 
  pivot_longer(
    cols = !gene_list,
    names_to = "overlapping_status",
    values_to = "count"
    )

# Check
predicted_input_gene_overlap
```

```{r Convert variables to appropriate class}
# Put variables to be converted to factors into a vector
factor_vars <- c(
  "gene_list",
  "overlapping_status"
)

# Convert variables to factor
predicted_input_gene_overlap[factor_vars] <- predicted_input_gene_overlap[factor_vars] %>% 
  map(as.factor)

# Change the count variable to be numeric
predicted_input_gene_overlap <- predicted_input_gene_overlap %>% 
  mutate(count = 
           as.numeric(count))

# Check
predicted_input_gene_overlap
```

```{r Change order of factor levels}
# Update factor levels
predicted_input_gene_overlap <- predicted_input_gene_overlap %>% 
  mutate(gene_list = 
           factor(gene_list, 
                  levels = c("GWAS", "DisGeNET", "Clinvar", "Union")
                  )
         )

predicted_input_gene_overlap <- predicted_input_gene_overlap %>% 
  mutate(overlapping_status = 
           factor(overlapping_status, 
                  levels = c("overlapping_predictions", "non_overlapping_predictions")
                  )
         )

# Check
predicted_input_gene_overlap %>% 
  map(levels)
```

```{r Calculate percentage of overlapping and non-overlapping genes}
predicted_input_gene_overlap <- predicted_input_gene_overlap %>% 
  group_by(gene_list) %>% 
  mutate(percent = 
           round(count/sum(count) * 100, 2))

# Check
predicted_input_gene_overlap
```

```{r Plot the overlap between the predicted genes and input genes}


predicted_input_gene_overlap %>% 
  ggplot(aes(x = gene_list, y = count, fill = overlapping_status)) +
  geom_bar(
    stat = "identity", 
    position = "stack",
    colour = "black"
    ) +
  geom_text(aes(label = ifelse(percent > 5, paste0(count, " (", percent, "%)"), "")), 
            position = position_stack(vjust = 0.5), size = 3) +
  labs(y = "Predicted gene count",
       x = "Gene list") +
  theme_minimal() +
  scale_fill_discrete(name = "Overlapping status",
                      labels = c("Predicted genes in other input list",
                                 "Predicted genes not in other input list")) +
  theme(axis.text.x = element_text(colour = "black"),
        axis.text.y = element_text(colour = "black"))


```
